### 2019-08-07 defesa/tex/appendix/3pnts_ellipse_1.tex
add2

\begin{equation}\label{eq:trpnts}
\hat{p}=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
\sin{\theta}&-\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right]
\end{equation}

@@

After replacing the trigonometric functions with \autoref{eq:trigId}, we get $\hat{p}_1, \hat{p}_2, \hat{p}_3$ as quotients of polynomials on $t$ of degree $2$.

@@

Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically. This ends halving the upper-bound to $6$.

>>>>

\begin{equation}\label{eq:trpnts}
\varphi(p)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right]
\end{equation}

@@

After replacing the trigonometric functions with \autoref{eq:trigId}, we get:

\begin{equation}
\varphi(p)=\left[\begin{array}{c}
\frac{b}{a}(\dfrac{t^2-1}{t^2+1}p_x + \dfrac{2t}{t^2+1}p_y)\\
\dfrac{t^2-1}{t^2+1}p_y - \dfrac{2t}{t^2+1}p_x\\
\end{array}\right],
\end{equation}

Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of polynomials on of degree $2$.

@@

Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically. This ends up halving the upper-bound to $6$.
